Last glacial cycle glacier erosion potential in the Alps \large \newline Supplementary figures

### 2021-06-11 articles/erosion/alps-erosion-supplement.tex
Add erosion hypsogram plots in supplement.

>>>>

    \begin{figure*}
      \centerline{\includegraphics{alpero_hypsogram}}
      \caption[
        Potential erosion rate per altitude band after
        \citet{Koppes.etal.2015}, same as main text Fig. 4.
      ]{%
        \textbf{(a)} Potential erosion rate ``hypsogram'', showing the
          geometric mean of modelled rates in 100-m elevation bands
          across the entire model domain and its time evolution. Hatches
          indicate elevation bands with fewer than a hundred grid cells
          (100\,$km^2$).
        \textbf{(b)} Distribution of model domain bedrock topography (grey
          bars) and glaciated topography (blue bars) in 100-m elevation bands,
          and the corresponding cumulative potential erosion volume (brown
          line).
        \textbf{(c)} Same as Fig.~\ref{fig:cumulative}b.
        After \citet{Koppes.etal.2015}, same as main text Fig. 4.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_hypsogram_her2015}
      \caption{%
        Potential erosion rate per altitude band after
        \citet{Herman.etal.2015}.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_hypsogram_hum1994}
      \caption{%
        Potential erosion rate per altitude band after
        \citet{Humphrey.Raymond.1994}.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_hypsogram_coo2020}
      \caption{%
        Potential erosion rate per altitude band after
        \citet{Cook.etal.2020}.}
    \end{figure*}
